Proportional multi-state multiple-cohort life table model

### 2018-04-04 MSLT/MSLTdoc.Rmd
R markdown not running code chunks
Fixed path for files

##### Prevent scientific notation in data frame

@@

##### Load all functions/packages

source("MSLT/code/functions.R")
```

@@

idata <- read.csv("MSLT/data/idata.csv", stringsAsFactors = F)
edata <- read.csv("MSLT/data/edata.csv", stringsAsFactors = F)
irr <- read.csv("MSLT/data/irr.csv", stringsAsFactors = F)
ee <- read.csv("MSLT/data/ee.csv", stringsAsFactors = F)
```

>>>>

# Prevent scientific notation in data frame

@@

#Load all functions/packages

source("code/functions.R")
```

@@

idata <- read.csv("data/idata.csv", stringsAsFactors = F)
edata <- read.csv("data/edata.csv", stringsAsFactors = F)
irr <- read.csv("data/irr.csv", stringsAsFactors = F)
ee <- read.csv("data/ee.csv", stringsAsFactors = F)
```
